\LARGE \bf A Teachable Robotic Agent for Children Learning Handwriting, Capable of Simulated Handwriting Itself

### 2014-11-27 main.tex
Don't allude to LBT novelty

Also notable, the robot is not used in the usual context of robotics or computer
education, but instead in an activity -- handwriting -- which requires fine
physical skills. In such activities, the embodied nature of the robot is appropriate as in interventions where motor mimicry is elicited \cite{Berninger1997} the arm motion for instance is, \emph{by
itself}, part of the teaching. Along these lines, we hope to see more research
on non-STEM educational applications of robotics.

Beyond handwriting, we believe that this work provides a novel perspective on
the role for robots in the field of education. \emph{Learning by teaching} is a
powerful paradigm because of not only its pedagogical efficacy, but its
potential to positively impact the child's motivation and self-esteem. We hope that 
this article shows that this is a very relevant context of use for robots. Indeed,
when facing a child with school difficulties, robots can play the role of a na\"ive 
learner which neither adults nor peers -- because of the social effects it would 
induce -- can convincingly play.

>>>>

Also notable, the robot is not used in the usual context of robotics or computer
education, but instead in an activity -- handwriting -- which requires fine
physical skills. In such activities, the embodied nature of the robot is appropriate as in interventions where motor mimicry is elicited \cite{Berninger1997} the arm motion for instance is, \emph{by
itself}, part of the teaching. Furthermore, when facing a child with school 
difficulties, robots can play the role of a na\"ive learner which neither adults 
nor peers -- because of the social effects it would induce -- can convincingly 
play. Along these lines, we hope to see more research
on non-STEM educational applications of robotics.

% Beyond handwriting, we believe that this work provides a novel perspective on
% the role for robots in the field of education. \emph{Learning by teaching} is a
% powerful paradigm because of not only its pedagogical efficacy, but its
% potential to positively impact the child's motivation and self-esteem. We hope that 
% this article shows that this is a very relevant context of use for robots. Indeed,
% when facing a child with school difficulties, robots can play the role of a na\"ive 
% learner which neither adults nor peers -- because of the social effects it would 
% induce -- can convincingly play.
